Galaxy Zoo: Morphological Classifications for Galaxies in HST Legacy Imaging

### 2016-04-15 writeup/gz_hubble_data.tex
Small text changes to the higher-order branches

\textit{Usual due diligence for an intro science paper. Should cover:}

@@

The unshaded regions in Figure~\ref{fig:6a} define discrete ranges of redshift, surface brightness, and \pfeatures{} a galaxy must have in order for the $\zeta$ approach to be confidentely applied to a galaxy in the GZH sample. While the appropriate correctable regions were defined discretely, we assume the true correctable region is a smooth function of z, $\mu$, and \pfeatures{}. To define this smooth space, we use a convex hull method to enclose the correctable and uncorrectable \ferengi{} galaxies is z-$\mu$-\pfeatures{} space. Due to scatter, the boundaries of the resulting hulls overlap. The boundaries are then adjusted until the contamination from both groups is minimized. We use the resulting hulls to define the correctable and uncorrectable regions for categorizing the \hst{} galaxies. The results of this method and final categorization of the \hst{} sample is displayed in Table~\ref{tbl:hubble_debiasable}. We find that of the galaxies at redshift higher than $z=z_{0}=0.3$, 17\% of these are able to be debiased using the $\zeta$ method, 27\% cannot be debiased, and 56\% cannot be determined, due to a lack of redshift or information or due to a lack of \ferengi{} data corresponding to those galaxies' redshift/surface brightness values.

@@

\subsection{Challenges of debiasing questions beyond ``smooth or features''}
Each FERENGI image does not have the same number of users answering each question, due to the structure of the decision tree. Every user answers the first question, ``Is the galaxy smooth and rounded, with no sign of a disk?''; as such the vote fractions $\rm p_{smooth}, p_{features}$, and $\rm p_{artifact}$ are all computed with the minimum statistical error for any question, with roughly 40 total answers (see Section~\ref{sec:gz_interface}). The number of users to answer any subsequent question, however, is always equal to or less than the number to answer the preceding question. For this reason, some galaxies may have very few (or even zero) answers to a question further down the tree (see Figure make-figure-of-count-distribution-for-each-question). To minimize statistical error in computing vote fractions, a cut on the number of answers to a given question is always implemented.

In the FERENGI data, we find that this places large limitations on the amount of information we can extract for the higher order questions. We require that at least 5 users answer each question for a galaxy image at $z=0.3$ \emph{and} its image at higher $z$. This requirement placed on both images is not met by a significant number of galaxies for questions beyond question 1. Without sufficient galaxies in each surface brightness/redshift bin, we cannot accurately measure a relationship between vote fractions and redshift; for this reason we only offer debiased vote fractions for question 1.

>>>>

@@

The unshaded regions in Figure~\ref{fig:6a} define discrete ranges of redshift, surface brightness, and \pfeatures{} a galaxy must have in order for the $\zeta$ approach to be confidentely applied to a galaxy in the GZH sample. While the appropriate correctable regions were defined discretely, we assume the true correctable region is a smooth function of z, $\mu$, and \pfeatures{}. To define this smooth space, we generate a convex hull that encloses the correctable and uncorrectable \ferengi{} galaxies in $z$-$\mu$-\pfeatures{} space. The boundaries are then adjusted until the contamination from both groups is minimized. We use the resulting hulls to define the correctable and uncorrectable regions for categorizing the \hst{} galaxies. The results of this method and final categorization of the \hst{} sample is displayed in Table~\ref{tbl:hubble_debiasable}. We find that of the galaxies at redshift higher than $z=z_{0}=0.3$, 17\% of these are able to be debiased using the $\zeta$ method, 27\% cannot be debiased, and 56\% cannot be determined, due to a lack of redshift or information or due to a lack of \ferengi{} data corresponding to those galaxies' redshift/surface brightness values.

@@

\subsection{Challenges of debiasing questions beyond ``smooth or features''}

As with the HST images, each FERENGI subject has a varying number of users answering the various questions in the hierarchical decision tree. Every user answers the first question, ``Is the galaxy smooth and rounded, with no sign of a disk?''; as such the vote fractions $\rm p_{smooth}, p_{features}$, and $\rm p_{artifact}$ are all computed with the minimum statistical error for any question, with roughly 40 total answers (see Section~\ref{sec:interface}). The number of users to answer any subsequent question, however, is always equal to or less than the number to answer the preceding question. The average number of responses per task for fourth- or fifth-tier questions such as spiral arm structure (Tasks 12--14) is only $4\pm4$ for the FERENGI sample; while this is distribution is strongly bimodal (reflecting the true morphologies of selected galaxies), the very low absolute numbers of votes introduce very high variance when attempting to calculate a statistical correction.

In the FERENGI data, these numbers severely limit the amount of information we can extract for the higher-tier questions. The debiasing technique used (Section~\ref{ssec:zeta}) require that at least 5~users answer each question for a galaxy image at $z=0.3$ \emph{and} its image at higher redshift. This requirement placed on both images is not met by a significant number of galaxies for questions beyond Task~01. The FERENGI images classified do not have sufficient numbers of objects in the surface brightness/redshift bins to accurately measure if the relation between vote fractions and redshift is single-valued.

for this reason we only offer debiased vote fractions for Task~01 (smooth/features/artifact).
